### 2017-02-07 writing/paper-Tian-gr-wetting.tex
Added the part for charge-induced 2D surface tension change

% Created 2017-01-17 Tue 11:30
% Intended LaTeX compiler: pdflatex
\documentclass[aps,prl,reprint,groupedaddress,amsmath,amssymb, showpacs]{revtex4-1}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{fontspec}
\date{}
\title{}
\begin{document}

@@

where \(\gamma_{\mathrm{2D-w}}\) is the surface tension between the
interface of the 2D material and the aqueous phase,
\(\gamma_{\mathrm{2D}}\) and \(\gamma_{\mathrm{w}}\) are the surface
tensions of the 2D material and water in vacuum,
respectively. \(\Phi_{\mathrm{2D-w}}\) is contributed by both the
short-range dispersion interaction and long-range electrostatic
interaction between the 2D material and water. The existence of
additional charges in 2D materials gives rise to the reorientation of
adjacent water molecules \cite{ostrowski_tunable_2014}. On the other
hand, the formation of electric double layer (EDL) in an ionic
solution near the interface also alters the interfacial adhesion
properties, known as the electrowetting effect \cite{Lippmann_1908},
which has been widely used in microfluidic applications
\cite{Mugele_2005}.  Owing to the additive nature of dispersion and
electrostatic interactions, we propose that the change of interfacial
adhesion energy \(\Delta \Phi_{\mathrm{2D-w}}\) is a combined effect of
the reorientation effect \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{or}}\) and EDL
formation \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\):
\begin{equation}
\label{eqn:contrib-adhesion-change}
\Delta \Phi_{\mathrm{2D-w}} = \Delta \Phi_{\mathrm{2D-w}}^{\mathrm{or}}
                              + \Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}
\end{equation}

@@

While the interfacial dispersion interaction vanishes several
molecules away from the surface, the long range electrostatic
interaction will cause the aqueous ions to rearrange at a much longer
length scale, forming an EDL at the interface and decrease the
interfacial surface tension by the phenomenon known as
electrowetting. To model the effect of electrowetting, we first
consider that a contamination layer with thickness \(d_{\mathrm{c}}\)
covers the 2D material surface. Since the airborne contaminants are
mostly hydrocarbon compounds, they can be treated as a dielectric
layer with permittivity \(\epsilon_{\mathrm{c}}\). We use the
Gouy-Chapman-Stern model to describe the EDL in the aqueous phase,
which consists a Helmholtz double layer with the same permittivity
\(\epsilon_{\mathrm{w}}\) as water, and thickness \(d_{\mathrm{H}}\),
together with a diffuse layer where ionic distribution is described by
the Gouy-Chapman equation.  The potentials at the surface of the 2D
material, the contamination layer surface and the outer Helmholtz
plane (the interface between the Helmholtz double layer and the
diffuse layer) are \(\psi_{\mathrm{2D}}^{*}\), \(\psi_{\mathrm{2D}}\) and
\(\psi_{\mathrm{L}}\), respectively. An illustration of the model for the
2D-material-water interface is shown in Fig. \ref{fig:scheme-EDL}.

@@

If we neglect specific adsorption of ions at the solid-liquid interface,
electroneutrality ensures that the charge density of the 2D material
\(\sigma_{\mathrm{2D}}\) balances the total charge density of the EDL
\(\sigma_{\mathrm{L}}\) \cite{bard_electrochemical_1980}:
\begin{equation}
\sigma_{\mathrm{2D}} + \sigma_{\mathrm{L}} = 0
\end{equation}
From the Gouy-Chapman model of symmetric electrolytes we know:
\begin{align}
\displaystyle
\label{eqn:psi-L}
\psi_{\mathrm{L}} &= -\frac{2k_{\mathrm{B}}T}{z_{0}e} 
                       \sinh^{-1}\left(
                         \frac{\sigma_{\mathrm{L}}}{\sqrt{8c_{0}N_{\mathrm{A}}\epsilon_{\mathrm{w}}k_{\mathrm{B}}T}}
                          \right) \\
\label{eqn:psi-2D}
\psi_{\mathrm{2D}} &= \psi_{\mathrm{L}} - \sigma_{\mathrm{L}}\frac{d_{\mathrm{H}}}{\epsilon_{\mathrm{w}}} \\
\psi_{\mathrm{2D}}^{*} &= \psi_{\mathrm{2D}} - \sigma_{\mathrm{L}}\frac{d_{\mathrm{c}}}{\epsilon_{\mathrm{c}}}
\end{align} 
where \(z_{0}\) is the valency of the electrolyte, \(c_{0}\) is the
concentration of the electrolyte, \(N_{\mathrm{A}}\) is the Avogadro
constant and \(k_{\mathrm{B}}\) is the Boltzmann constant. While the
contamination layer is responsible for a potential drop across the
solid phase, the solid-liquid interfacial potential
\(\psi_{\mathrm{2D}}\) which contributes to the \(\Delta \Phi_{\mathrm{2D-w}}^{el}\), is only governed by \(\sigma_{\mathrm{L}}\). Therefore
we conclude that the existence of a contamination layer does not affect
the magnitude of \(\Delta \Phi_{\mathrm{2D-w}}}^{el}\).

The change of interfacial adhesion energy is calculated using the
Gibbs adsorption isotherm equation:
\(\mathrm{d}\Phi_{\mathrm{2D-w}}^{el} = \mathrm{d}
\gamma_{\mathrm{2D-w}}^{el} = -z_{0}e\Gamma
\mathrm{d}\psi_{\mathrm{2D}}\), where \(\Gamma\) is the interfacial
adsorption number at the solid-liquid interface. Since the Debye
length is much smaller than the diameter of a macroscopic droplet,
\(\Gamma\) can be approximated by the total excessive charge density
\(\sigma_{\mathrm{L}}\) at the interface. Therefore \(\Delta
\Phi_{\mathrm{2D-2}}^{el}\) can be derived from Eqs (\ref{eqn:psi-2D})
and (\ref{eqn:psi-L}):
\begin{equation}
\label{eqn:Delta-Phi-exact}
\begin{aligned}
\Delta \Phi_{\mathrm{2D-w}}^{el}
&= -\int_{0}^{\psi_{\mathrm{2D}}} \sigma_{\mathrm{L}} \mathrm{d}\psi' \\
&= -\int_{0}^{\sigma_{\mathrm{L}}} \sigma'\left(
   \frac{1}{C_{\mathrm{H}}} + \frac{1}{C_{\mathrm{L}}}
                                          \right) \mathrm{d}\sigma' \\
&= -\frac{\sigma_{\mathrm{L}}^{2}}{2C_{\mathrm{H}}}
    -\sqrt{\frac{32k_{\mathrm{B}}^{3}T^{3} \epsilon_{\mathrm{w}} c_{0} N_{\mathrm{A}}}{z_{0}^{2}e^{2}}}
   \left[\cosh(\frac{z_{0}e\psi_{\mathrm{L}}}{2k_{\mathrm{B}}T}) - 1\right] \\
&= -\frac{\sigma_{\mathrm{L}}^{2}}{2C_{\mathrm{H}}} 
   - \frac{\sigma_{\mathrm{L}}^{2}}{C_{\mathrm{L}} 
   + \frac{\epsilon_{w}}{\lambda_{\mathrm{D}}}}
\end{aligned}
\end{equation}
where \(C_{\mathrm{H}}=\epsilon_{w}/d_{\mathrm{H}}\) is the geometric
capacitance of the Helmholtz double layer,
\(C_{\mathrm{L}}=\sqrt{\frac{2z_{0}^{2}e^{2}\epsilon_{\mathrm{w}}c_{0}N_{\mathrm{A}}}{k_{\mathrm{B}}T}}
\cosh (\frac{z_{0}e\psi_{\mathrm{L}}}{2k_{\mathrm{B}}T})\) is the
capacitance of diffuse layer derived from the Gouy-Chapman equation,
and
\(\lambda_{\mathrm{D}}=\sqrt{\frac{\epsilon_{\mathrm{w}}k_{\mathrm{B}}T}{2z^{2}e^{2}c_{0}N_{\mathrm{A}}}}\)
is the Debye length of the electrolyte. The quantity
\(\epsilon_{\mathrm{w}}/\lambda_{\mathrm{D}}\) is actually the
Debye-Hückel-style capacitance of the EDL.
Eq. (\ref{eqn:Delta-Phi-exact}) shows that \(\Delta
\Phi_{\mathrm{2D-w}}^{el}\) consists of the contributions from the
Helmholtz double layer and the diffuse layer, respectively.  Note that
at room temperature, when \(\sigma_{\mathrm{2D}}\) is large
(e.g. \(10^{13}\) \(e\cdot \mathrm{cm}^{-2}\)) and \(c_{0}\) is small
(e.g. \(10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\)),
\(\psi_{\mathrm{L}}\)=347 mV
, which is much larger than \(k_{\mathrm{B}}T/e\), causing a significant
discrepancy between the Gouy-Chapman capacitance \(C_{\mathrm{L}}\) and
the Debye-Hückel capacitance
\(\epsilon_{\mathrm{w}}/\lambda_{\mathrm{D}}\). This effect is often
ignored in previous studies concerning the electrowetting on graphene
and other 2D materials
\cite{ostrowski_tunable_2014,daub_electrowetting_2007,goniszewski_correlation_2016,ashraf_doping-induced_2016},
and the classical Young-Lippman equation \(\Delta
\gamma=-\frac{1}{2}C\psi^{2}\) (or \(\Delta
\gamma=-\frac{\sigma^{2}}{2C}\)) is casually used instead, assuming the
capacitance to be constant. Since most of the reported samples deals with pure water with extremely low \(c_{0}\), the Debye-Hückel capacitance is much smaller than the Gouy-Chapman capacitance, leading to an overestimation of \(\Delta\cos\theta\). Therefore our
derivation in Eq. \ref{eqn:Delta-Phi-exact} provides a more accurate
approach to analyze \(\Delta \Phi_{\mathem{2D-w}}^{el}\) as a function of \(\sigma_{\mathrm{2D}}\).

@@

It should also be noted that in electrowetting experiments
where additional charge is doped to the 2D material via dielectric
layer \cite{hong_mechanism_2016}, the initial doping density
\(\sigma_{\mathrm{i}}\) should also be considered to explain the
asymmetric electrowetting behavior. In an electrowetting system where a
dielectric layer with geometric capacitance \(C_{\mathrm{d}}\) and external
voltage \(V_{\mathrm{2D}}\) is applied to the 2D material, the doping
density in the 2D material is calculated as \cite{tian_multiscale_2016}:
\begin{equation}
\label{eqn:doping-vm-2D}
V_{\mathrm{2D}} = \frac{\sigma_{\mathrm{2D}} - \sigma_{\mathrm{i}}} {C_{\mathrm{d}}} 
                 + \int_{\sigma_{\mathrm{i}}}^{\sigma_{\mathrm{2D}}} 
                   \frac{1}{C_{\mathrm{2D}}} \mathrm{d}\sigma'
\end{equation}
where \(C_{\mathrm{2D}}\) is the quantum capacitance of the 2D material, which is proportional to the density of states (DOS) \(g(E)\) at energy level \(E\): \(C_{\mathrm{2D}}=g(E)e^{2}\).

@@

\begin{align}
\label{eqn:dV-sigma-2D}
\mathrm{d} V_{\mathrm{2D}} &= \left(\frac{1}{C_{\mathrm{d}}} +
\frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d}\sigma_{\mathrm{2D}} \\
\label{eqn:dpsi-sigma-L}
\mathrm{d} \psi_{\mathrm{2D}} &= -\left( \frac{1}{C_{\mathrm{H}}}
+ \frac{1}{C_{\mathrm{L}}} \right) \mathrm{d}\sigma_{\mathrm{L}}
\end{align}
and by substituting \(\sigma_{\mathrm{2D}} = -\sigma_{\mathrm{L}}\), we derive the ratio between \(\psi_{\mathrm{2D}}\) and \(V_{\mathrm{2D}}\), named as \(\beta\):
\begin{equation}
\label{eqn:beta}
\beta = \frac{\mathrm{d} \psi_{\mathrm{2D}}}{\mathrm{d}
V_{\mathrm{2D}}} = \dfrac{\dfrac{1}{C_{\mathrm{L}}} +
\dfrac{1}{C_{\mathrm{H}}}}{\dfrac{1}{C_{\mathrm{d}}} + \dfrac{1}{C_{\mathrm{2D}}}}
\end{equation}
at a certain \(c_{0}\), the larger \(\beta\) is, the higher tunability in
wettability of the 2D material will be. On the device side, it can be
achieved if both \(C_{\mathrm{d}}\) and \(C_{\mathrm{2D}}\) are
larger. Increasing the value of \(C_{\mathrm{2D}}\) can be implemented
by replacing graphene--a 2D semimetal, with a 2D semiconductor, such
as TMDC \cite{tian_multiscale_2016}. Here we evaluate a
2D-material-based electrowetting device consists of a 2 nm thick HfO\(_{\text{2}}\)
dielectric layer with \(\epsilon_{\mathrm{d}}=24.0\), and an 2D material sheet
selected from graphene, silicene (2D allotrope of Si), germanene (2D
allotrope of Ge), MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\) and WTe\(_{\text{2}}\) (see
Fig. \ref{fig:dcos-all-2D}(a)). The DOS and \(C_{\mathrm{2D}}\) are
calculated from first-principle simulations using HSE06 hydrid
functional (see Ref. \cite{tian_multiscale_2016}). The magnitude of \(\Delta \cos \theta\) as a function of \(V_{\mathrm{2D}}\) in devices based on different 2D materials is shown in Fig. \ref{fig:dcos-all-2D}(b).
\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{../img/dcos-all-2D.pdf}
\caption{\label{fig:dcos-all-2D}
(a) Schematic illustration of the 2D-material-based electrowetting device. (b) \(\Delta\cos\theta\) as a function of \(V_{\mathrm{2D}}\) for selected 2D materials.}
\end{figure}

>>>>

% Created 2017-02-07 Tue 22:04
% Intended LaTeX compiler: pdflatex
\documentclass[aps,prl,reprint,groupedaddress,amsmath,amssymb, showpacs]{revtex4-1}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{fontspec}
\date{}
\title{}
\begin{document}

@@

where \(\gamma_{\mathrm{2D-w}}\) is the surface tension between the
interface of the 2D material and the aqueous phase,
\(\gamma_{\mathrm{2D}}\) and \(\gamma_{\mathrm{w}}\) are the surface
tensions of the 2D material and water in air,
respectively.

\(\Phi_{\mathrm{2D-w}}\) is contributed by both the
short-range dispersion interaction and long-range electrostatic
interaction between the 2D material and water. The existence of
additional charges in 2D materials gives rise to the reorientation of
adjacent water molecules \cite{ostrowski_tunable_2014}. On the other
hand, the formation of electric double layer (EDL) in an ionic
solution near the interface also alters the interfacial adhesion
properties, known as the electrowetting effect \cite{Lippmann_1908},
which has been widely used in microfluidic applications
\cite{Mugele_2005}.  Owing to the additive nature of dispersion and
electrostatic interactions, we propose that the change of interfacial
adhesion energy \(\Delta \Phi_{\mathrm{2D-w}}\) is a combined effect of
the reorientation effect \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{or}}\) and EDL
formation \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\):
\begin{equation}
\label{eqn:contrib-adhesion-change}
\Delta \Phi_{\mathrm{2D-w}} = \Delta \Phi_{\mathrm{2D-w}}^{\mathrm{or}}
                              + \Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}
\end{equation}

@@

While the interfacial dispersion interaction vanishes several
molecules away from the surface, the long range electrostatic
interaction will cause the aqueous ions to rearrange at a much longer
length scale, forming an EDL at the interface and decrease the
interfacial surface tension by the phenomenon known as electrowetting.
Revisiting Eq. (\ref{eqn:def-adhesion}), we know that the change of
interfacial tension due to electrostatic interactions, \(\Delta
\Phi_{\mathrm{2D-w}}^{\mathrm{el}}\), is given by:

\begin{equation}
\label{eqn:Delta-Phi-el-def}
\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}} = \Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}
                                           -\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}
                                           -\Delta \gamma_{\mathrm{w}}^{\mathrm{el}}
\end{equation}
where \(\Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}\), \(\Delta
\gamma_{\mathrm{2D}}^{\mathrm{el}}\) and \(\Delta
\gamma_{\mathrm{w}}^{\mathrm{el}}\) denote the change of surface
tension of 2D material-water interface, 2D material-air and
water-air, respectively. In the continuum model, all the changes of
surface tensions can be modeled by surface excesses. From the
isothermal 2D Gibbs-Duhem equation we can calculate the change of surface
energy \(\mathrm{d} \gamma\):

\begin{equation}
\label{eqn:iso-gibbs-duhem}
\displaystyle
\mathrm{d}\gamma = -\frac{\sum_{\mathrm{i}} n_{\mathrm{i}}^{\mathrm{ex}}}{A} \mathrm{d} \mu_{\mathrm{i}} 
                 = -\sum_{\mathrm{i}} \Gamma_{i} \mathrm{d} \mu_{\mathrm{i}}
\end{equation}
where \(n_{\mathrm{i}}^{\mathrm{ex}}\) is the surface excess amount of
specie i, \(A\) is the unit are of the surface, \(\Gamma_{\mathrm{i}}\) is
the surface excess concentration of specie i, and \(\mu_{\mathrm{i}}\)
is the chemical potential of specie i. Eq. (\ref{eqn:iso-gibbs-duhem})
indicates that: both the charges accumulated on the 2D material
surface and the formation of electric double layer will alter the
interfacial tension of 2D materials. As far as we are concerned, the
effect of charge-induced surface tension change of 2D materials has
rarely been addressed previously. For a charged 2D material surface in
air, the decrease of surface tension equals the work required to
charge the isolated 2D material:

\begin{equation}
\label{eqn:dgamma-QC}
\begin{aligned}
\mathrm{d} \gamma_{\mathrm{2D}}^{\mathrm{el}} &= -\Gamma_{e} \mathrm{d} E_{\mathrm{F}} \\
                                              &= -\frac{\sigma_{\mathrm{2D}}}{C_{\mathrm{2D}}} \mathrm{d}\sigma_{\mathrm{2D}}
\end{aligned}
\end{equation}
where \(E_{\mathrm{F}}=\mu_{e}\) is the Fermi level of the 2D material
(equals the chemical potential of electrons in the 2D materials) and
\(C_{\mathrm{2D}}\) is the quantum capacitance of the 2D material, which
is proportional to the density of states (DOS) \(g(E_{\mathrm{F}})\) at
Fermi level \(E_{\mathrm{F}}\):
\(C_{\mathrm{2D}}=g(E_{\mathrm{F}})e^{2}\). Due to the fact that most 2D
materials possess quantum capacitances essentially smaller than those
of bulk materials, one would expect that the charge-induced-decrease
of surface tension of 2D materials is more prominent than bulk
materials. Here we demonstrate the degree of charge-induced
surface tension decrease of several typical 2D materials in
air. The selected 2D materials are graphene, silicene (2D allotrope
of Si), germanene (2D allotrope of Ge), MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\) and
WTe\(_{\text{2}}\), respectively. Their DOS as functions of \(E_{\mathrm{F}}\) have been previously
reported by density functional theory (DFT) calculation, based on the
HSE06 hybrid functional approach \cite{tian_multiscale_2016}. The
charge-induced decrease of surface tension of the 2D materials
\(\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}\), as a function of the
surface charge density \(\sigma_{\mathrm{2D}}\), is shown in Fig. \ref{fig:dgamma-sigma}.
\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{../img/dgamma-sigma.pdf}
\caption{\label{fig:dgamma-sigma}
\(\Delta \gamma_{\mathrm{2D}}^{\mathrm{el}}\) as a function of \(\sigma_{\mathrm{2D}}\) for several 2D materials: graphene, silicene, germanene, MoS\(_{2}\), MoTe\(_{2}\), WS\(_{2}\) and WTe\(_{2}\)}
\end{figure}
It can be observed from our calculations that graphene has the largest
degree of surface tension decrease (ca. 22 mJ\(\cdot\mathrm{m}^{-2}\)
when \(\sigma_{\mathrm{2D}}=\pm5\times10^{13}\ e\cdot
\mathrm{cm}^{-2}\)), due to the fact that graphene has the lowest
\(C_{\mathrm{2D}}\) among the selected 2D materials
\cite{tian_multiscale_2016}. We can rationalize the \(\Delta
\gamma_{\mathrm{2D}}^{\mathrm{el}}\) - \(\sigma_{\mathrm{2D}}\) relation
of the 2D materials by their \(C_{\mathrm{2D}}\) values: the 2D
semimetals (graphene, silicene and germanene) generally have larger
decrease of surface tension, compared with the semiconducting 2D TMDCs
at same doping level, due to the limited DOS dispersion in 2D
semimetals. Notably, the results indicate that a significant decrease
of surface tension of 2D materials (at the order of 10 mJ\(\cdot
\mathrm{m}^{-2}\)) can be achieved with a doping at the order of
\(10^{13}\ e\cdot \mathrm{cm}^{-2}\), and may eventually be experimentally
observed.

Similarly, \(\Delta \gamma_{\mathrm{2D-w}}^{\mathrm{el}}\) is
contributed by both the 2D surface charge and the charge accumulation
in the EDL:

\begin{equation}
\label{eqn:dgamma-2D-w}
\mathrm{d}\gamma_{\mathrm{2D-w}}^{\mathrm{el}} = -\frac{\sigma_{\mathrm{2D}}}{e} \mathrm{d}E_{\mathrm{F}}
-\sum_{\mathrm{i}} z_{\mathrm{i}}e\Gamma_{\mathrm{i}}^{\mathrm{s}} \mathrm{d}\psi_{\mathrm{2D}}
\end{equation}
where \(\Gamma_{\mathrm{i}}^{\mathrm{s}}\) and \(z_{\mathrm{i}}\) are the
surface excess concentration and valency of ionic solute i,
respectively; \(\psi_{\mathrm{2D}}\) is the electrostatic potential at the 2D
material-water interface. On the other hand \(\gamma_{\mathrm{w}}\) is
independent of the surface charge of the 2D material, since no surface
excess is present at the water-air interface. We therefore derive
the expression for \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) as
follows:

\begin{equation}
\label{eqn:Delta-Phi-final}
\begin{aligned}
\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}} &= -\frac{\sigma_{\mathrm{2D}}}{e}dE_{\mathrm{F}} 
                                             -\sum_{\mathrm{i}} z_{\mathrm{i}}e\Gamma_{\mathrm{i}}^{\mathrm{s}} \mathrm{d}\psi_{\mathrm{2D}}
                                             +\frac{\sigma_{\mathrm{2D}}}{e}dE_{\mathrm{F}} \\
                                          &= -\sigma_{\mathrm{L}} \mathrm{d}\psi_{\mathrm{2D}}
\end{aligned}
\end{equation}
where \(\sigma_{\mathrm{L}}\) is the total charge density in the EDL. As
the accumulation of charge on the 2D material surface occurs both on
the 2D material-air and 2D material-water interfaces, their
contributions to the surface tension is canceled out. As a result
\(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) is governed by the ion
accumulation in EDL alone, in consistent with the trivial
electrowetting theory (constant solid surface tension). However, the
absolute values of \(\gamma_{\mathrm{2D-w}}\) and \(\gamma_{\mathrm{2D}}\)
do change due to the aforementioned phenomenon.

To evaluate the effect of electrowetting, we first
consider that a contamination layer with thickness \(d_{\mathrm{c}}\)
covers the 2D material surface. Since the airborne contaminants are
mostly hydrocarbon compounds, they can be treated as a dielectric
layer with permittivity \(\epsilon_{\mathrm{c}}\). We use the
Gouy-Chapman-Stern model to describe the EDL in the aqueous phase,
which consists a Helmholtz double layer with the same permittivity
\(\epsilon_{\mathrm{w}}\) as water, and thickness \(d_{\mathrm{H}}\),
together with a diffuse layer where ionic distribution is described by
the Gouy-Chapman equation.  The potentials at the surface of the 2D
material, the contamination layer surface and the outer Helmholtz
plane (the interface between the Helmholtz double layer and the
diffuse layer) are \(\psi_{\mathrm{2D}}^{*}\), \(\psi_{\mathrm{2D}}\) and
\(\psi_{\mathrm{L}}\), respectively. An illustration of the model for the
2D-material-water interface is shown in Fig. \ref{fig:scheme-EDL}.

@@

If we neglect specific adsorption of ions at the solid-liquid interface,
electroneutrality ensures that the charge density of the 2D material
\(\sigma_{\mathrm{2D}}\) balances the total charge density of the EDL
\(\sigma_{\mathrm{L}}\) \cite{bard_electrochemical_1980}:
\begin{equation}
\sigma_{\mathrm{2D}} + \sigma_{\mathrm{L}} = 0
\end{equation}
From the Gouy-Chapman model of 1 symmetric electrolyte we know:
\begin{align}
\displaystyle
\label{eqn:psi-L}
\psi_{\mathrm{L}} &= -\frac{2k_{\mathrm{B}}T}{z_{0}e} 
                       \sinh^{-1}\left(
                         \frac{\sigma_{\mathrm{L}}}{\sqrt{8c_{0}N_{\mathrm{A}}\epsilon_{\mathrm{w}}k_{\mathrm{B}}T}}
                          \right) \\
\label{eqn:psi-2D}
\psi_{\mathrm{2D}} &= \psi_{\mathrm{L}} - \sigma_{\mathrm{L}}\frac{d_{\mathrm{H}}}{\epsilon_{\mathrm{w}}} \\
\psi_{\mathrm{2D}}^{*} &= \psi_{\mathrm{2D}} - \sigma_{\mathrm{L}}\frac{d_{\mathrm{c}}}{\epsilon_{\mathrm{c}}}
\end{align} 
where \(z_{0}\) is the valency of the electrolyte, \(c_{0}\) is the
concentration of the electrolyte, \(N_{\mathrm{A}}\) is the Avogadro
constant and \(k_{\mathrm{B}}\) is the Boltzmann constant. While the
contamination layer is responsible for a potential drop across the
solid phase, the solid-liquid interfacial potential
\(\psi_{\mathrm{2D}}\) which contributes to the \(\Delta \Phi_{\mathrm{2D-w}}^{el}\), is only governed by \(\sigma_{\mathrm{L}}\). Therefore
we conclude that the existence of a contamination layer does not affect
the magnitude of \(\Delta \Phi_{\mathrm{2D-w}}}^{el}\).

The exact solution of \(\Delta
\Phi_{\mathrm{2D-w}}^{el}\) can be derived from Eqs (\ref{eqn:psi-2D})
and (\ref{eqn:psi-L}):
\begin{equation}
\label{eqn:Delta-Phi-exact}
\begin{aligned}
\Delta \Phi_{\mathrm{2D-w}}^{el}
&= -\int_{0}^{\psi_{\mathrm{2D}}} \sigma_{\mathrm{L}} \mathrm{d}\psi' \\
&= -\int_{0}^{\sigma_{\mathrm{L}}} \sigma'\left(
   \frac{1}{C_{\mathrm{H}}} + \frac{1}{C_{\mathrm{L}}}
                                          \right) \mathrm{d}\sigma' \\
&= -\frac{\sigma_{\mathrm{L}}^{2}}{2C_{\mathrm{H}}}
    -\sqrt{\frac{32k_{\mathrm{B}}^{3}T^{3} \epsilon_{\mathrm{w}} c_{0} N_{\mathrm{A}}}{z_{0}^{2}e^{2}}}
   \left[\cosh(\frac{z_{0}e\psi_{\mathrm{L}}}{2k_{\mathrm{B}}T}) - 1\right] \\
&= -\frac{\sigma_{\mathrm{L}}^{2}}{2C_{\mathrm{H}}} 
   - \frac{\sigma_{\mathrm{L}}^{2}}{C_{\mathrm{L}} 
   + \frac{\epsilon_{w}}{\lambda_{\mathrm{D}}}}
\end{aligned}
\end{equation}
where \(C_{\mathrm{H}}=\epsilon_{w}/d_{\mathrm{H}}\) is the geometric
capacitance of the Helmholtz double layer,
\(C_{\mathrm{L}}=\sqrt{\frac{2z_{0}^{2}e^{2}\epsilon_{\mathrm{w}}c_{0}N_{\mathrm{A}}}{k_{\mathrm{B}}T}}
\cosh (\frac{z_{0}e\psi_{\mathrm{L}}}{2k_{\mathrm{B}}T})\) is the
capacitance of diffuse layer derived from the Gouy-Chapman equation,
and
\(\lambda_{\mathrm{D}}=\sqrt{\frac{\epsilon_{\mathrm{w}}k_{\mathrm{B}}T}{2z^{2}e^{2}c_{0}N_{\mathrm{A}}}}\)
is the Debye length of the electrolyte. The quantity
\(\epsilon_{\mathrm{w}}/\lambda_{\mathrm{D}}\) is actually the
Debye-Hückel-style capacitance of the EDL.
Eq. (\ref{eqn:Delta-Phi-exact}) shows that \(\Delta
\Phi_{\mathrm{2D-w}}^{el}\) consists of the contributions from the
Helmholtz double layer and the diffuse layer, respectively.  Note that
at room temperature, when \(\sigma_{\mathrm{2D}}\) is large
(e.g. \(10^{13}\) \(e\cdot \mathrm{cm}^{-2}\)) and \(c_{0}\) is small
(e.g. \(10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\)),
\(\psi_{\mathrm{L}}\)=347 mV
, which is much larger than \(k_{\mathrm{B}}T/e\), causing a significant
discrepancy between the Gouy-Chapman capacitance \(C_{\mathrm{L}}\) and
the Debye-Hückel capacitance
\(\epsilon_{\mathrm{w}}/\lambda_{\mathrm{D}}\). This effect is often
ignored in previous studies concerning the electrowetting on graphene
and other 2D materials
\cite{ostrowski_tunable_2014,daub_electrowetting_2007,goniszewski_correlation_2016,ashraf_doping-induced_2016},
and the classical Young-Lippman equation \(\Delta
\gamma=-\frac{1}{2}C\psi^{2}\) (or \(\Delta
\gamma=-\frac{\sigma^{2}}{2C}\)) is casually used instead, assuming the
capacitance to be constant. Since most of the reported samples deals with pure water with extremely low \(c_{0}\), the Debye-Hückel capacitance is much smaller than the Gouy-Chapman capacitance, leading to an overestimation of \(\Delta\cos\theta\). Therefore our
derivation in Eq. \ref{eqn:Delta-Phi-exact} provides a more accurate
approach to analyze \(\Delta \Phi_{\mathrm{2D-w}}^{\mathrm{el}}\) as a function of \(\sigma_{\mathrm{2D}}\).

@@

It should also be noted that in electrowetting experiments
where additional charge is doped to the 2D material via dielectric
layer \cite{hong_mechanism_2016}, the initial doping density
\(\sigma_{\mathrm{i}}\) should also be considered to explain the
asymmetric electrowetting behavior. In an electrowetting system where a
dielectric layer with geometric capacitance \(C_{\mathrm{d}}\) and external
voltage \(V_{\mathrm{2D}}\) is applied to the 2D material, the doping
density in the 2D material is calculated as \cite{tian_multiscale_2016}:
\begin{equation}
\label{eqn:doping-vm-2D}
V_{\mathrm{2D}} = \frac{\sigma_{\mathrm{2D}} - \sigma_{\mathrm{i}}} {C_{\mathrm{d}}} 
                 + \int_{\sigma_{\mathrm{i}}}^{\sigma_{\mathrm{2D}}} 
                   \frac{1}{C_{\mathrm{2D}}} \mathrm{d}\sigma'
\end{equation}

@@

\begin{align}
\label{eqn:dV-sigma-2D}
\mathrm{d} V_{\mathrm{2D}} &= \left(\frac{1}{C_{\mathrm{d}}} +
\frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d}\sigma_{\mathrm{2D}} \\
\label{eqn:dpsi-sigma-L}
\mathrm{d} \psi_{\mathrm{2D}} &= -\left( \frac{1}{C_{\mathrm{H}}}
+ \frac{1}{C_{\mathrm{L}}} \right) \mathrm{d}\sigma_{\mathrm{L}}
\end{align}
and by substituting \(\sigma_{\mathrm{2D}} = -\sigma_{\mathrm{L}}\), we derive the ratio between \(\psi_{\mathrm{2D}}\) and \(V_{\mathrm{2D}}\), named as \(\beta\):
\begin{equation}
\label{eqn:beta}
\beta = \frac{\mathrm{d} \psi_{\mathrm{2D}}}{\mathrm{d}
V_{\mathrm{2D}}} = \dfrac{\dfrac{1}{C_{\mathrm{L}}} +
\dfrac{1}{C_{\mathrm{H}}}}{\dfrac{1}{C_{\mathrm{d}}} + \dfrac{1}{C_{\mathrm{2D}}}}
\end{equation}
at a certain \(c_{0}\), the larger \(\beta\) is, the higher tunability in
wettability of the 2D material will be. On the device side, it can be
achieved if both \(C_{\mathrm{d}}\) and \(C_{\mathrm{2D}}\) are
larger. Increasing the value of \(C_{\mathrm{2D}}\) can be implemented
by replacing graphene--a 2D semimetal, with a 2D semiconductor, such
as TMDC \cite{tian_multiscale_2016}. Here we evaluate a
2D-material-based electrowetting device consists of a 2 nm thick HfO\(_{\text{2}}\)
dielectric layer with \(\epsilon_{\mathrm{d}}=24.0\), and an 2D material
sheet selected from graphene, silicene, germanene, MoS\(_{\text{2}}\), MoTe\(_{\text{2}}\), WS\(_{\text{2}}\)
and WTe\(_{\text{2}}\) (see Fig. \ref{fig:dcos-all-2D}(a)). The magnitude of \(\Delta
\cos \theta\) as a function of \(V_{\mathrm{2D}}\) in devices based on
different 2D materials is shown in Fig. \ref{fig:dcos-all-2D}(b).
\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{../img/dcos-all-2D.pdf}
\caption{\label{fig:dcos-all-2D}
(a) Schematic illustration of the 2D-material-based electrowetting device. (b) \(\Delta\cos\theta\) as a function of \(V_{\mathrm{2D}}\) for selected 2D materials.}
\end{figure}
